---
title: "Data Engineering 2: Cloud Computing"
subtitle: "Sentiment Analysis of Different Bible versions using AWS"
author: "CEU Student 2200147"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  prettydoc::html_pretty:
    highlight: github
    theme: cayman
    toc: yes
---

```{r}
rm(list=ls())
```

# Load libraries

```{r}
library(rvest)
library(readr)
library(stringr)
library(aws.comprehend)
library(dplyr)
library(ggplot2)
```


# Function for extracting sentiment

Make function to extract sentiment:

```{r}
extract_sentiment <- function(file_path){
  # Reading txt file
  txtfile <- read_file(file_path)
  # Cleaning - removing \n and ""
  cleanedtext <- gsub("\n", "", txtfile, fixed = TRUE)
  # Cleaning - merging multiple spaces into a single space
  cleanedtext <- str_replace(gsub("\\s+", " ", str_trim(cleanedtext)), "B", "b")
  # Converting txt to bytes
  byte.counter <- nchar(cleanedtext, type = "bytes")
  cat("Total bytes: " , byte.counter, "\n")
  xiteration <-  byte.counter %/% 5000
  cat("Number of full iterations: " , xiteration, "\n")
  remainder.count <- (xiteration - (byte.counter / 5000)) * -1
  cat("Remainder of bytes: ", remainder.count, "\n")
  full.iter <- byte.counter / 5000
  cat("Full iteration: ", full.iter, "\n")
  five.k.iterations <- byte.counter / full.iter
  cat("5000 byte iterations: " , five.k.iterations, "\n", "\n")
  # Breaking the input text into character vectors of length.segm characters each
  char.segments <- function(x, segm.length){
      byte.counter <- nchar(x, type = 'bytes')
      f <- c(1, rep(0, segm.length - 1))
      f <- cumsum(rep(f, length.out = byte.counter))
      s <- split(unlist(strsplit(x,'')), f)
      unname(sapply(s, paste, collapse = ''))
  }
  five.thousand.byte.chunk <- char.segments(cleanedtext, 5000)
  count.of.five.thousand <- nchar(five.thousand.byte.chunk, type = "bytes")
  # Setting up vectors
  sentiment_vector = c() 
  positive_vector = c()
  negative_vector = c()
  # Setting variable for the loop
  count = 0
  # Iterating through the chunks 
  for (i in 1:(full.iter+1)) { 
      if (five.thousand.byte.chunk[i] > "") {
          count = count + 1
          df <- detect_sentiment(five.thousand.byte.chunk[i])
          # Extract sentiments
          sentiment_vector <- c(sentiment_vector, as.character(df$Sentiment))
          # Extract positivity score 
          positive_vector <- c(positive_vector, df$Positive)
          # Extract negativity score 
          negative_vector <- c(negative_vector, df$Negative)
      }
  }
  df_out <- cbind(positive_vector, negative_vector, sentiment_vector)
  return(df_out)
}
```

Test first on a single text source:

```{r}
# file_path <- "Bible_Texts/01_King_James_bible.txt"
# df_test <- data.frame(extract_sentiment(file_path))
# str(df_test)
```

```{r}
txt_files <- list.files("Bible_Texts/")
txt_files
list_of_txt_file_paths <- paste0("Bible_Texts/", txt_files)
list_of_txt_file_paths
```

```{r}
all_data <- c()
```


Now for the 4 texts we can perform sentiment analysis using the following for loop and save the results to a single data frame:

```{r}
for (i in 1:length(list_of_txt_file_paths)) {
  all_data <- rbind(all_data, (data.frame(extract_sentiment(list_of_txt_file_paths[i]), i )))
}
```

Some cleaning up:

```{r}
df_final <- all_data %>% mutate(positive_vector = as.numeric(positive_vector),
                                negative_vector = as.numeric(negative_vector))
```

Some plots:

```{r}
library(scales)
color <- c("#3a5e8cFF", "#10a53dFF", "#541352FF", "#ffcf20FF", "#2f9aa0FF")
#blue  #3a5e8c   # purple #541352    teal #2f9aa0  yellow #ffcf20   # green #10a53d
show_col(color)
df_final$col <- as.character(color[df_final$i])
```
# Plots

```{r}
# Plotting the scores
ggplot(data = df_final) +
  geom_point(aes(x = positive_vector, y = negative_vector, color = col), alpha = 0.3)  + 
  scale_colour_identity() + #makes colours read properly
  geom_point(aes(x=mean(as.numeric(df_final$positive_vector[df_final$i == 1])),
                 y=mean(as.numeric(df_final$negative_vector[df_final$i == 1]))), 
             colour=color[1], shape = 3, size = 7, stroke = 3) +
  geom_point(aes(x=mean(as.numeric(df_final$positive_vector[df_final$i == 2])),
                 y=mean(as.numeric(df_final$negative_vector[df_final$i == 2]))), 
             colour=color[2], shape = 3, size = 7, stroke = 3) +
  geom_point(aes(x=mean(as.numeric(df_final$positive_vector[df_final$i == 3])),
                 y=mean(as.numeric(df_final$negative_vector[df_final$i == 3]))), 
             colour=color[3], shape = 3, size = 7, stroke = 3) +
  geom_point(aes(x=mean(as.numeric(df_final$positive_vector[df_final$i == 4])),
                 y=mean(as.numeric(df_final$negative_vector[df_final$i == 4]))), 
             colour=color[4], shape = 3, size = 7, stroke = 3) +
  ggtitle("Positive vs negative sentiments in different biblical versions") +
  xlab("Positive sentiments") +
  ylab("Negative sentiments") +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1))  +
  theme_bw() + 
  geom_label( 
    label="King James Bible", 
    x=0.9,
    y=0.9,
    label.padding = unit(0.55, "lines"), # Rectangle size around label
    label.size = 0.25,
    color = "white",
    fill= color[1]
  ) + 
  geom_label( 
    label="World English Bible", 
    x=0.9,
    y=0.8,
    label.padding = unit(0.55, "lines"), # Rectangle size around label
    label.size = 0.25,
    color = "black",
    fill= color[2]
  ) + 
  geom_label( 
    label="English Bible", 
    x=0.9,
    y=0.7,
    label.padding = unit(0.55, "lines"), # Rectangle size around label
    label.size = 0.25,
    color = "White",
    fill= color[3]
  ) + 
  geom_label( 
    label="Github Bible", 
    x=0.9,
    y=0.6,
    label.padding = unit(0.55, "lines"), # Rectangle size around label
    label.size = 0.25,
    color = "black",
    fill= color[4]
  )
```

```{r}
ggplot(data = df_final)  +
  geom_boxplot(aes(x = i, y = positive_vector, fill = col)) +
  labs(title = "Boxplot for positive scores in Biblical versions", 
       x = "Bible version", 
       y = "Log-transformed positive scores" ) +
  scale_y_continuous(limits = c(0, 1)) +
  scale_y_log10() +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 11L, hjust = 0.5, face = "bold"),
    legend.position = "none")  +
  geom_hline(yintercept = mean(as.numeric(df_final$positive_vector[df_final$i == 1])), size = 0.4, col = "darkgreen") +
  geom_hline(yintercept = mean(as.numeric(df_final$positive_vector[df_final$i == 2])), size = 0.4, col = "red") +
  geom_hline(yintercept = mean(as.numeric(df_final$positive_vector[df_final$i == 3])), size = 0.4, col = "blue") +
  geom_hline(yintercept = mean(as.numeric(df_final$positive_vector[df_final$i == 4])), size = 0.4, col = "purple") +
  scale_x_discrete(limits = c("King James Bible", "World English Bible", "English Bible","Github Bible"))
```

```{r}
ggplot(data = df_final)  +
  geom_boxplot(aes(x = i, y = negative_vector, fill = col)) +
  labs(title = "Boxplot for negative scores in Biblical texts", 
       x = "Bible version", 
       y = "Log-transformed negative scores" ) +
  scale_y_continuous(limits = c(0, 1)) +
  scale_y_log10() +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 11L, hjust = 0.5, face = "bold"),
    legend.position = "none")  +
  geom_hline(yintercept = mean(as.numeric(df_final$positive_vector[df_final$i == 1])), size = 0.4, col = "darkgreen") +
  geom_hline(yintercept = mean(as.numeric(df_final$positive_vector[df_final$i == 2])), size = 0.4, col = "red") +
  geom_hline(yintercept = mean(as.numeric(df_final$positive_vector[df_final$i == 3])), size = 0.4, col = "blue") +
  geom_hline(yintercept = mean(as.numeric(df_final$positive_vector[df_final$i == 4])), size = 0.4, col = "purple") +
  scale_x_discrete(limits = c("King James Bible", "World English Bible", "English Bible","Github Bible"))
```

```{r}
ggplot(data = df_final, aes(x = negative_vector, fill = col)) +
  geom_histogram( bins = 50) + 
  labs(title = "Histogram for negative scores in different versions", 
       x = "Negative sentiments", 
       y =  "Count",
       fill = "Bible version")  +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 11L, hjust = 0.5, face = "bold"), 
    legend.position = "none")  +
  scale_fill_manual(values=color) + 
  geom_label( 
    label="King James Bible", 
    x=0.85,
    y=600,
    label.padding = unit(0.35, "lines"), # Rectangle size around label
    label.size = 0.25,
    color = "white",
    fill= color[1]
  ) + 
  geom_label( 
    label="World English Bible", 
    x=0.85,
    y=500,
    label.padding = unit(0.35, "lines"), # Rectangle size around label
    label.size = 0.25,
    color = "black",
    fill= color[2]
  ) + 
  geom_label( 
    label="English Bible", 
    x=0.85,
    y=400,
    label.padding = unit(0.35, "lines"), # Rectangle size around label
    label.size = 0.25,
    color = "White",
    fill= color[3]
  ) + 
  geom_label( 
    label="Github Bible", 
    x=0.85,
    y=300,
    label.padding = unit(0.35, "lines"), # Rectangle size around label
    label.size = 0.25,
    color = "black",
    fill= color[4]
  )
```

```{r}
ggplot(data = df_final, aes(x = positive_vector, fill = col)) +
  geom_histogram(bins = 50) + 
  labs(title = "Histogram for positive scores in different versions", 
       x = "Positive sentiments", 
       y =  "Count",
       fill = "Bible version")  +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 11L, hjust = 0.5, face = "bold"), 
    legend.position = "none")  +
  scale_fill_manual(values=color) + 
  geom_label( 
    label="King James Bible", 
    x=0.85,
    y=600,
    label.padding = unit(0.35, "lines"), # Rectangle size around label
    label.size = 0.25,
    color = "white",
    fill= color[1]
  ) + 
  geom_label( 
    label="World English Bible", 
    x=0.85,
    y=500,
    label.padding = unit(0.35, "lines"), # Rectangle size around label
    label.size = 0.25,
    color = "black",
    fill= color[2]
  ) + 
  geom_label( 
    label="English Bible", 
    x=0.85,
    y=400,
    label.padding = unit(0.35, "lines"), # Rectangle size around label
    label.size = 0.25,
    color = "White",
    fill= color[3]
  ) + 
  geom_label( 
    label="Github Bible", 
    x=0.85,
    y=300,
    label.padding = unit(0.35, "lines"), # Rectangle size around label
    label.size = 0.25,
    color = "black",
    fill= color[4]
  )
```

```{r}
ggplot(data = df_final, aes(x = negative_vector, fill = col)) +
  geom_density(alpha = 0.5) + 
  labs(title = "Density plot for negative scores in different versions", 
       x = "Negative sentiments", 
       y =  "Density",
       fill = "Bible version")  +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 11L, hjust = 0.5, face = "bold"), legend.position = "none")  +
  scale_fill_manual(values=color) +
  geom_vline(xintercept = mean(as.numeric(df_final$negative_vector[df_final$i == 1])), size = 0.4, col = color[1]) +
  geom_vline(xintercept = mean(as.numeric(df_final$negative_vector[df_final$i == 2])), size = 0.4, col = color[2]) +
  geom_vline(xintercept = mean(as.numeric(df_final$negative_vector[df_final$i == 3])), size = 0.4, col = color[3]) +
  geom_vline(xintercept = mean(as.numeric(df_final$negative_vector[df_final$i == 4])), size = 0.4, col = color[4]) +
  scale_x_log10()
```


```{r}
ggplot(data = df_final, aes(x = positive_vector, fill = col)) +
  geom_density(alpha = 0.5) + 
  labs(title = "Density plot for positive scores in different versions", 
       x = "Positive sentiments", 
       y =  "Density",
       fill = "Bible version")  +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 11L, hjust = 0.5, face = "bold"), legend.position = "none")  +
  scale_fill_manual(values=color) +
  geom_vline(xintercept = mean(as.numeric(df_final$positive_vector[df_final$i == 1])), size = 0.4, col = color[1]) +
  geom_vline(xintercept = mean(as.numeric(df_final$positive_vector[df_final$i == 2])), size = 0.4, col = color[2]) +
  geom_vline(xintercept = mean(as.numeric(df_final$positive_vector[df_final$i == 3])), size = 0.4, col = color[3]) +
  geom_vline(xintercept = mean(as.numeric(df_final$positive_vector[df_final$i == 4])), size = 0.4, col = color[4]) +
  scale_x_log10()
```

# T-test and ANOVA

In the following sections, to satisfy the condition of normality of the residuals before performing a series of tests, the data will be log-transformed so as to resemble a gaussian distribution. The QQ-plots show that this was a fairly good transformation and thus the test results can be used.

## T-tests

We perform a series of T-tests with a 95% confidence interval for paired vectors from different bible versions. The differences in texts can be said to be statistically significant when the p value is high.

```{r}
Ttest1_2 <- t.test(as.numeric(log(df_final$negative_vector[df_final$i == 1])), log(as.numeric(df_final$negative_vector[df_final$i == 2])), alternative = "two.sided")
Ttest1_2 
Ttest1_3 <- t.test(log(as.numeric(df_final$negative_vector[df_final$i == 1])), log(as.numeric(df_final$negative_vector[df_final$i == 3])), alternative = "two.sided")
Ttest1_3
Ttest1_4 <- t.test(log(as.numeric(df_final$negative_vector[df_final$i == 1])), log(as.numeric(df_final$negative_vector[df_final$i == 4])), alternative = "two.sided")
Ttest1_4 
Ttest2_3 <- t.test(log(as.numeric(df_final$negative_vector[df_final$i == 2])), log(as.numeric(df_final$negative_vector[df_final$i == 3])), alternative = "two.sided")
Ttest2_3
Ttest2_4 <- t.test(log(as.numeric(df_final$negative_vector[df_final$i == 2])), log(as.numeric(df_final$negative_vector[df_final$i == 4])), alternative = "two.sided")
Ttest2_4 
Ttest3_4 <- t.test(log(as.numeric(df_final$negative_vector[df_final$i == 3])), log(as.numeric(df_final$negative_vector[df_final$i == 4])), alternative = "two.sided")
Ttest3_4 
```

No difference between 1 and 3.

```{r}
Ttest1_2 <- t.test(as.numeric(log(df_final$positive_vector[df_final$i == 1])), log(as.numeric(df_final$positive_vector[df_final$i == 2])), alternative = "two.sided")
Ttest1_2 
Ttest1_3 <- t.test(log(as.numeric(df_final$positive_vector[df_final$i == 1])), log(as.numeric(df_final$positive_vector[df_final$i == 3])), alternative = "two.sided")
Ttest1_3
Ttest1_4 <- t.test(log(as.numeric(df_final$positive_vector[df_final$i == 1])), log(as.numeric(df_final$positive_vector[df_final$i == 4])), alternative = "two.sided")
Ttest1_4 
Ttest2_3 <- t.test(log(as.numeric(df_final$positive_vector[df_final$i == 2])), log(as.numeric(df_final$positive_vector[df_final$i == 3])), alternative = "two.sided")
Ttest2_3
Ttest2_4 <- t.test(log(as.numeric(df_final$positive_vector[df_final$i == 2])), log(as.numeric(df_final$positive_vector[df_final$i == 4])), alternative = "two.sided")
Ttest2_4 
Ttest3_4 <- t.test(log(as.numeric(df_final$positive_vector[df_final$i == 3])), log(as.numeric(df_final$positive_vector[df_final$i == 4])), alternative = "two.sided")
Ttest3_4 
```

No difference between 1 and 4, 2 and 3 (for positive scores).

Still, the t-test is most likely not the appropriate test as the number of data points we have is quite high - the t-test is usually used for smaller samples as its tails are quite heavy and allow for wider confidence intervals.

## ANOVA tests

Only the ANOVA can help us to make inference about the population given the sample at hand, and help us to answer the initial research question “Is the sentiment different between the 4 versions of the Bible?”.

```{r}
oneway.test(log(negative_vector) ~ i,
  data = df_final,
  var.equal = FALSE # assuming non-equal variances
)
```

```{r}
oneway.test(log(positive_vector) ~ i,
  data = df_final,
  var.equal = FALSE # assuming non-equal variances
)
```

```{r}
res_aov <- aov(log(negative_vector) ~ i,
  data = df_final,
)
summary(res_aov)
library(car)
qqPlot(res_aov$residuals,
  id = FALSE,
  ylab = ("AOV residuals"),
  xlab= ("normalised quantiles")) + # id = FALSE to remove point identification
  title("QQ Plot for log(negative scores)")
```

```{r}
res_aov <- aov(log(positive_vector) ~ i,
  data = df_final,
)
summary(res_aov)
qqPlot(res_aov$residuals,
  id = FALSE,
  ylab = ("AOV residuals"),
  xlab= ("normalised quantiles")) + # id = FALSE to remove point identification
  title("QQ Plot for log(positive scores)")
```

From the density and QQ-plots above, we can already see that the normality assumption seems to be met. The points in the QQ-plots roughly follow the straight line and most of them are within the confidence bands, also indicating that residuals follow approximately a normal distribution.

Given that the p-value is smaller than 0.05 for the negative scores, we reject the null hypothesis, so we reject the hypothesis that all means are equal. Therefore, we can conclude that at least one version is different than the others in terms of negative scores (p-value = 9.56e-07).

Given that the p-value is higher than 0.05 for the positive scores, we cannot reject the null hypothesis, and conclude that all means are equal. Therefore, we can conclude that all four versions of the Bible are equally positive (p-value = 0.161).



